---
title: "Borden"
output:
  html_document:
    df_print: paged
  pdf_document: 
    fig_caption: yes
    keep_tex: yes
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE,dev="png",fig.asp=0.46^(-1),dpi=100,fig.height =150)
##knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE,dev="png",fig.asp=0.46,dpi=100,fig.height =100)
```


#### Model: GEOtop v3.0
Compiler: c++ (gcc 5.4.0 "c++ (Ubuntu 5.4.0-6ubuntu1~16.04.9) 5.4.0 20160609")
Processor: Intel(R) Core(TM) i7-6700HQ CPU @ 2.60GHz
Author:  Elisa Bortoli (elisa.bortoli3@gmail.com)
Date: 28-06-2018

#### Name:  Borden05m
Description: Borden Experiment (initial waterdepth 20cm below ditch outlet -
rainfall intensity 20 mm/hr duration 50 min). Inspired by the Borden test Case
a well known small catchment laboratory experiment (@Vanderkwaak2000,@Abdul1989).





#### Results published in:

The GEOtop 2.0 version (branch se27xx) has been tested to simulate runoff and water content in the soil. 
Results published in @Kollet2017. 

The following simulated variables have  been simulated and tested against observations:

```
Output:
- tabs (6): every 1 min (basin,discharge,point,soiltemp,soilwater)
- maps (66): every 6 min (Prec,psiliq,thetaliq,waterchan,watersurf,watertable)
```


#### Simulation duration:

```
InitDateDDMMYYYYhhmm   = 01/06/2000 12:00
EndDateDDMMYYYYhhmm    = 01/06/2000 12:10

### Output:
PointOutputFile = "output-tabs/surface"
```

```{r eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}
library(dplyr)
library(geotopbricks)
library(magrittr)
library(reshape2)
library(stringr)
library(purrr)
##library(dplyr)

wpath <- '/home/ecor/activity/2020/geotop_examples/GEOtopExamples-1/tests/Borden05m/sims'
wpaths <- wpath %>% list.files(pattern="sim",full.name=TRUE)
names(wpaths) <- wpath %>% list.files(pattern="sim",full.name=FALSE)
tz <- "GMT" ###Etc/GMT-1"
add_suffix_dir="_v3"
date_field <- "DATE.day.month.year.hour.min."
discharge <-  "DischargeFile" %>% get.geotop.inpts.keyword.value(wpath=wpaths[1],data.frame=TRUE,date_field=date_field,tz=tz,formatter="",add_suffix_dir=add_suffix_dir)

start <- "InitDateDDMMYYYYhhmm" %>% get.geotop.inpts.keyword.value(wpath=wpaths[1],date=TRUE,tz=tz)
time <- (index(discharge)-start) %>% as.numeric(unit="secs")
discharge <- as.data.frame(discharge)
discharge$time <- time
discharge$Qout.m3.s. <- discharge$Qoutlandsup.m3.s.+discharge$Qoutlandsub.m3.s.

vars <- c("Qout.m3.s.") ###,"Vsup.Dt.m3.s.","Vsub.Dt.m3.s.","Vchannel.m3.") Vsup e Vsup non funzionano?
discharge <- discharge %>% melt(id="time") %>% filter(variable %in% vars)
discharge$variable <- as.character(discharge$variable) %>% factor()
# [1] "t.days."           "JDfrom0"           "JD"                "Qtot.m3.s."        "Vsup.Dt.m3.s."     "Vsub.Dt.m3.s."    
# [7] "Vchannel.m3."      "Qoutlandsup.m3.s." "Qoutlandsub.m3.s." "Qoutbottom.m3.s."  "time"             
discharge$sim <- names(wpaths)[1]

```




### Observations:


Discharge time series.

```{r eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}



borden_obs_csv <- '/home/ecor/activity/2020/geotop_examples/GEOtopExamples-1/tests/Borden05m/obss/discharge.csv'
obs <- borden_obs_csv %>% read.table(sep=",",header=TRUE) %>% dplyr::select(1,2)
names(obs) <- c("time","Qout.m3.s.")
var_obs <- names(obs)[-1]
obs <- obs %>% melt(id="time")
obs$sim <- "obs"

##nobs <-  obs$variable %>% unique() %>% as.character()
discharge <- rbind(discharge,obs[,names(discharge)])  %>% filter(!is.na(value))

```

### Comparison

Here is a comparison plot:

```{r Comparison,eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE,fig.height=5000}

###{r Winter_2001_2002,echo=FALSE,out.width='90%', fig.align='center', fig.cap=NULL, fig.height=5,results='asis',warning=FALSE}

library(ggplot2)
library(dplyr)
library(lubridate)
library(purrr)
##library(RColorBrewer)

####  https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=8
color_obs <- "black"
###colors <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5",color_obs)
colors <- c("blue",color_obs)
names(colors) <- discharge$sim %>% unique()

if (colors["obs"]!=color_obs) {
   
   colors[names(colors)!="obs"] <- colors[colors!=color_obs]
   colors["obs"] <- color_obs
   
}
alphas <- array(0.5,length(colors))
names(alphas) <- names(colors)
alphas["obs"] <- 1
####

# year <- 2001
# start <- "%04d-08-01" %>% sprintf(year) %>% as.Date()
# end <- start+years(1)
# 
# pointc <- point %>% filter(variable %in% nobs) %>% filter(time >= start & time<=end)

g <- ggplot()+geom_line(aes(x=time,y=value,group=sim,color=sim,alpha=sim),data=discharge)+theme_bw()+facet_grid(variable ~ .,scales="free_y")
g <- g+scale_color_manual(values=colors)+scale_alpha_manual(values=alphas)
g
```

Goodness of fit: 

```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE} 

library(hydroGOF)

### https://stackoverflow.com/questions/41861739/r-interpolate-a-data-table-when-xs-are-the-names-of-columns-and-ys-the-rows
timex <- discharge %>% filter(variable %in% var_obs)  %>% filter(sim=="obs")
timex <- tapply(X=timex$time,INDEX=timex$variable,FUN=function(x){x})

discharge_list <- list() 

for (itsim in unique(discharge$sim)) {
  
  timex <- discharge %>% filter(sim=="obs")
  x <- discharge %>% filter(sim==itsim)
  discharge_list[[itsim]] <- list()
  for (itvar in unique(x$variable)) {
    xv <- x %>% filter(variable==itvar)
    timexv <- timex %>% filter(variable==itvar) %>% dplyr::select(time) %>% extract2(1)
    out <- approx(x=xv$time,y=xv$value,xout=timexv) ## ADDITIONAL ARGUMENT TO ADD 
    out <- out %>% as.data.frame()
    names(out) <- c("time","value")
    out$variable <- itvar
    out$sim <- itsim
    out <- out[,names(xv)]
    discharge_list[[itsim]][[itvar]] <- out
  }  
    
    
    
}

id <- c("time","variable","value","sim")
dischargedd <- discharge_list %>% melt(id=id) %>% dplyr::select(-L1,-L2)


# discharge_dd <- discharge %>% filter(variable %in% var_obs) %>% filter(!is.na(value)) %>% group_by(sim,variable) %>% transmute(time=timex[[variable[1]]],value=approx(x=time,y=value,xout=timex[[variable[1]]]))
# 
# stop("HERE")

##obsc <- dischargedd %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value) %>% left_join(obsc) %>% ##as.data.frame()


obsc <- dischargedd %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value)
pointd <- dischargedd %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame()

oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})  

sims <- sapply(oo,FUN=function(x){x[1,"sim"]})
oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))}) 

oo <- oo %>% do.call(what=rbind)
rownames(oo) <- NULL
knitr::kable(oo)


```






<!-- Goodness of fit:  -->

<!-- ```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE}  -->

<!-- library(hydroGOF) -->


<!-- obsc <- pointc %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value) -->
<!-- pointd <- pointc %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame() -->

<!-- oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})   -->

<!-- sims <- sapply(oo,FUN=function(x){x[1,"sim"]}) -->
<!-- oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))})  -->

<!-- oo <- oo %>% do.call(what=rbind) -->
<!-- rownames(oo) <- NULL -->
<!-- knitr::kable(oo) -->

<!-- ``` -->







### References

```{r generateBibliography,echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE,print=FALSE,results="hide"}
require("knitcitations")
cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "bibliography.bib")

