---
title: "Col de la Porte"
output:
  pdf_document: 
    fig_caption: yes
    keep_tex: yes
  html_document:
    df_print: paged
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE,dev="png",fig.asp=0.46^(-1),dpi=100,fig.height =150)
##knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE,dev="png",fig.asp=0.46,dpi=100,fig.height =100)
```


#### Model: GEOtop v3.0
Compiler: gcc version 4.8.4 (Ubuntu 4.8.4-2ubuntu1~14.04.1) 
Processor: Intel(R) Core(TM) i7-5500U CPU @ 2.40GHz
Author: Stefano Endrizzi (stefano.end@gmail.com),Emanuele Cordano (emanuele.cordano@rendena100.eu)
Date: 25-11-2016

#### Name: ColdelaPorte
Description: Simulation 1D over the Col de la Porte dataset to test the capability of GEOotp to simulate snow depth, snow water equivalent, soil temperature.



#### Results published in:

First result with GEOtop v 2.0 are illustrated in the report XXX  (@Endrizzi2014 , supplemantary material). 
The following simulated variables have  been tested against observations:

- Liquid Precipitation Intensity (Rain); 

- Solid Precipitation Intensity (Snow);

- Snow Height (Snow Dapth);

- Snow Water Equivalent;

- Soil Temperature at 10 cm depth;

- Soil temparature at 20 cm depth;

- Soil Temparature at 50 cm depth;

- Surface Temparature ;

- Albedo .



<!-- - *Endrizzi S., Gruber S., Dall’Amico M., Rigon R., GEOtop 2.0.: Simulating the combined energy and water balance at and below the land surface accounting for soil freezing, snow cover and terrain effects, Geosci. Model Dev., 2014* -->

<!-- ![ColdelaPorte Example Results of GEOtop 2.0 (not reproducible)](images/Geotop-ColDePorte_Endrizzi2014.pdf) -->



#### Simulation duration:

```
InitDateDDMMYYYYhhmm   = 01/01/1997 00:00
EndDateDDMMYYYYhhmm    = 31/12/2011 23:00

### Output:
PointOutputFile = "output-tabs/surface"
```

```{r eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}
library(dplyr)
library(geotopbricks)
library(magrittr)
library(reshape2)
wpath <- '/home/ecor/activity/2020/geotop_examples/GEOtopExamples-1/tests/ColdelaPorte/sims' 
wpaths <- wpath %>% list.files(pattern="sim",full.name=TRUE)
names(wpaths) <- wpath %>% list.files(pattern="sim",full.name=FALSE)

outvar <- c("Tair.C.","Tsurface.C.","snow_depth.mm.","snow_water_equivalent.mm.","SWin.W.m2.","SWbeam.W.m2","SWdiff.W.m2.","SWnet.W.m2.","SWup.W.m2.","Psnow_under_canopy.mm.","Prain_under_canopy.mm.","Albedo") ###        "Prain_rain_on_snow.mm." 
date_field <- "Date12.DDMMYYYYhhmm."
tz <- "GMT" ###Etc/GMT-1"
add_suffix_dir="_v3"
####

point <- NULL
##tempz <- list()


for (it in names(wpaths)) {
   
   wpath <- wpaths[it]
   o <- get.geotop.inpts.keyword.value("PointOutputFile",data.frame=TRUE,wpath=wpath,add_suffix_dir=add_suffix_dir,date_field=date_field,tz=tz)
  ### ALBEDO COMPUTATION
   o$Albedo <-  o$SWup.W.m2 / o$SWin.W.m2.
   ###
   time <- index(o)
   o <- as.data.frame(o)
   o$time <- as.POSIXct(time)
   o <- o %>% melt(id="time") 
   o <- o %>% filter(variable %in% outvar)
   o$sim <- it
   point <- rbind(point,o)
   o <- get.geotop.inpts.keyword.value("SoilAveragedTempProfileFile",data.frame=TRUE,wpath=wpath,zlayer.formatter="z%04d",add_suffix_dir=add_suffix_dir,date_field=date_field,tz=tz)
  
   ###
   
   time <- index(o)
   o <- as.data.frame(o)
   o$time <- as.POSIXct(time)
   o <- o %>% melt(id="time")
   o$variable <- paste0("temp",o$variable)
   o$sim <- it
  point <- rbind(point,o)
   
}

str(point)

```




### Observations:


Snow heigth mm, Snow Water Equivalent mm(NOT FOUND), T surface C, T soil 10cm C,T soil 20cm C,T soil 50cm C
see @Morin2012.
<!-- - *Morin, S., Lejeune, Y., Lesaffre, B., Panel, J.-M., Poncet, D., David, -->
<!-- P., and Sudul, M.: An 18-yr long (1993–2011) snow and meteorological dataset from a mid-altitude mountain site (Col de Porte, -->
<!-- France, 1325 m alt.) for driving and evaluating snowpack models, Earth Syst. Sci. Data, 4, 13–21, doi:10.5194/essd-4-13-2012, -->
<!-- 2012.* -->

```{r eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}

library(stringr)
library(purrr)
library(dplyr)

cdp_obs_rda <- '/home/ecor/activity/2020/geotop_examples/GEOtopExamples-1/tests/ColdelaPorte/obss/rda/cdp_obs.rda'
load(cdp_obs_rda)

var_temp <-  c("Tsoil_10cm","Tsoil_20cm","Tsoil_50cm","Tsurf") 
var_snow <- c("Snowdepth")
var_swe <- c("SWE_pit")
var_prec <- c("Rainf","Snowf")
var_Albedo <- "Albedo"
var <- c(var_temp,var_snow,var_swe,var_prec,var_Albedo)
obs <- cdp_obs %>% filter(variable %in% var)  
obs$unit <- as.character(obs$unit)
### 
isd <- which(obs$variable %in% var_snow)
obs$value[isd] <- (obs$value[isd])*10
obs$unit[isd] <- "mm"
 ###head()

itemp <-  which(obs$variable %in% var_temp)
obs$value[itemp] <- (obs$value[itemp])-273.15 ####T(C) = T(K) - 273.15 ...
obs$unit[itemp] <- "C"

iswe <- which(obs$variable %in% var_swe)

obs$value[iswe] <- (obs$value[iswe])/1000*1000 ## From kg m-2 to mm
obs$unit[iswe] <- "mm"

iprec <- which(obs$variable %in% var_prec)
obs$value[iprec] <- obs$value[iprec]*3600/1000*1000  ## kg m-2 s-1 to mm/hr 
##"Psnow_under_canopy.mm.","Prain_under_canopy.mm."



levels(obs$variable)[levels(obs$variable)=="Snowdepth"] <- "snow_depth.mm."
levels(obs$variable)[levels(obs$variable)=="SWE_pit"] <- "snow_water_equivalent.mm."
levels(obs$variable)[levels(obs$variable)=="Tsurf"] <- "Tsurface.C."
levels(obs$variable)[levels(obs$variable)=="Tsoil_10cm"] <- "tempz0010"
levels(obs$variable)[levels(obs$variable)=="Tsoil_20cm"] <- "tempz0020"
levels(obs$variable)[levels(obs$variable)=="Tsoil_50cm"] <- "tempz0050"
levels(obs$variable)[levels(obs$variable)=="Rainf"] <- "Prain_under_canopy.mm."
levels(obs$variable)[levels(obs$variable)=="Snowf"] <- "Psnow_under_canopy.mm."
names(obs)[names(obs)=="Time"] <- "time"
obs$sim <- "obs"

nobs <-  obs$variable %>% unique() %>% as.character()
point <- rbind(point,obs[,names(point)])  %>% filter(!is.na(value))

```

### Winter 2001/2002

Here is a comparison plot:

```{r Winter_2001_2002,eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE,fig.height=5000}

###{r Winter_2001_2002,echo=FALSE,out.width='90%', fig.align='center', fig.cap=NULL, fig.height=5,results='asis',warning=FALSE}

library(ggplot2)
library(dplyr)
library(lubridate)
library(purrr)
##library(RColorBrewer)

####  https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=8
color_obs <- "black"
colors <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5",color_obs)
names(colors) <- point$sim %>% unique()

if (colors["obs"]!=color_obs) {
   
   colors[names(colors)!="obs"] <- colors[colors!=color_obs]
   colors["obs"] <- color_obs
   
}
alphas <- array(0.5,length(colors))
names(alphas) <- names(colors)
alphas["obs"] <- 1
####

year <- 2001
start <- "%04d-08-01" %>% sprintf(year) %>% as.Date()
end <- start+years(1)

pointc <- point %>% filter(variable %in% nobs) %>% filter(time >= start & time<=end)

g <- ggplot()+geom_line(aes(x=time,y=value,group=sim,color=sim,alpha=sim),data=pointc)+theme_bw()+facet_grid(variable ~ .,scales="free_y")
g <- g+scale_color_manual(values=colors)+scale_alpha_manual(values=alphas)
g
```

Goodness of fit: 

```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE} 

library(hydroGOF)


obsc <- pointc %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value)
pointd <- pointc %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame()

oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})  

sims <- sapply(oo,FUN=function(x){x[1,"sim"]})
oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))}) 

oo <- oo %>% do.call(what=rbind)
rownames(oo) <- NULL
knitr::kable(oo)

```







### Winter 2002/2003

Here is a comparison plot:

```{r Winter_2002_2003,eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}

###{r echo=FALSE,out.width='90%', fig.align='center', fig.cap=NULL, fig.height=5,results='asis',warning=FALSE}

library(ggplot2)
library(dplyr)
library(lubridate)
library(purrr)
##library(RColorBrewer)

####  https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=8
color_obs <- "black"
colors <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5",color_obs)
names(colors) <- point$sim %>% unique()

if (colors["obs"]!=color_obs) {
   
   colors[names(colors)!="obs"] <- colors[colors!=color_obs]
   colors["obs"] <- color_obs
   
}
alphas <- array(0.5,length(colors))
names(alphas) <- names(colors)
alphas["obs"] <- 1
####

year <- 2002
start <- "%04d-08-01" %>% sprintf(year) %>% as.Date()
end <- start+years(1)

pointc <- point %>% filter(variable %in% nobs) %>% filter(time >= start & time<=end)

g <- ggplot()+geom_line(aes(x=time,y=value,group=sim,color=sim,alpha=sim),data=pointc)+theme_bw()+facet_grid(variable ~ .,scales="free_y")
g <- g+scale_color_manual(values=colors)+scale_alpha_manual(values=alphas)
g
```

Goodness of fit: 

```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE} 

library(hydroGOF)


obsc <- pointc %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value)
pointd <- pointc %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame()

oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})  

sims <- sapply(oo,FUN=function(x){x[1,"sim"]})
oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))}) 

oo <- oo %>% do.call(what=rbind)
rownames(oo) <- NULL
knitr::kable(oo)

```





### Winter 2003/2004

Here is a comparison plot:

```{r Winter_2003_2004,eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}

###{r echo=FALSE,out.width='90%', fig.align='center', fig.cap=NULL, fig.height=5,results='asis',warning=FALSE}

library(ggplot2)
library(dplyr)
library(lubridate)
library(purrr)
##library(RColorBrewer)

####  https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=8
color_obs <- "black"
colors <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5",color_obs)
names(colors) <- point$sim %>% unique()

if (colors["obs"]!=color_obs) {
   
   colors[names(colors)!="obs"] <- colors[colors!=color_obs]
   colors["obs"] <- color_obs
   
}
alphas <- array(0.5,length(colors))
names(alphas) <- names(colors)
alphas["obs"] <- 1
####

year <- 2003
start <- "%04d-08-01" %>% sprintf(year) %>% as.Date()
end <- start+years(1)

pointc <- point %>% filter(variable %in% nobs) %>% filter(time >= start & time<=end)

g <- ggplot()+geom_line(aes(x=time,y=value,group=sim,color=sim,alpha=sim),data=pointc)+theme_bw()+facet_grid(variable ~ .,scales="free_y")
g <- g+scale_color_manual(values=colors)+scale_alpha_manual(values=alphas)
g
```

Goodness of fit: 

```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE} 

library(hydroGOF)


obsc <- pointc %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value)
pointd <- pointc %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame()

oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})  

sims <- sapply(oo,FUN=function(x){x[1,"sim"]})
oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))}) 

oo <- oo %>% do.call(what=rbind)
rownames(oo) <- NULL
knitr::kable(oo)

```








### Winter 2004/2005

Here is a comparison plot:

```{r Winter_2004_2005,eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}

###{r echo=FALSE,out.width='90%', fig.align='center', fig.cap=NULL, fig.height=5,results='asis',warning=FALSE}

library(ggplot2)
library(dplyr)
library(lubridate)
library(purrr)
##library(RColorBrewer)

####  https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=8
color_obs <- "black"
colors <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5",color_obs)
names(colors) <- point$sim %>% unique()

if (colors["obs"]!=color_obs) {
   
   colors[names(colors)!="obs"] <- colors[colors!=color_obs]
   colors["obs"] <- color_obs
   
}
alphas <- array(0.5,length(colors))
names(alphas) <- names(colors)
alphas["obs"] <- 1
####

year <- 2004
start <- "%04d-08-01" %>% sprintf(year) %>% as.Date()
end <- start+years(1)

pointc <- point %>% filter(variable %in% nobs) %>% filter(time >= start & time<=end)

g <- ggplot()+geom_line(aes(x=time,y=value,group=sim,color=sim,alpha=sim),data=pointc)+theme_bw()+facet_grid(variable ~ .,scales="free_y")
g <- g+scale_color_manual(values=colors)+scale_alpha_manual(values=alphas)
g
```

Goodness of fit: 

```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE} 

library(hydroGOF)


obsc <- pointc %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value)
pointd <- pointc %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame()

oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})  

sims <- sapply(oo,FUN=function(x){x[1,"sim"]})
oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))}) 

oo <- oo %>% do.call(what=rbind)
rownames(oo) <- NULL
knitr::kable(oo)

```












### Winter 2005/2006

Here is a comparison plot:

```{r Winter_2005_2006,eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}

###{r echo=FALSE,out.width='90%', fig.align='center', fig.cap=NULL, fig.height=5,results='asis',warning=FALSE}

library(ggplot2)
library(dplyr)
library(lubridate)
library(purrr)
##library(RColorBrewer)

####  https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=8
color_obs <- "black"
colors <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5",color_obs)
names(colors) <- point$sim %>% unique()

if (colors["obs"]!=color_obs) {
   
   colors[names(colors)!="obs"] <- colors[colors!=color_obs]
   colors["obs"] <- color_obs
   
}
alphas <- array(0.5,length(colors))
names(alphas) <- names(colors)
alphas["obs"] <- 1
####

year <- 2005
start <- "%04d-08-01" %>% sprintf(year) %>% as.Date()
end <- start+years(1)

pointc <- point %>% filter(variable %in% nobs) %>% filter(time >= start & time<=end)

g <- ggplot()+geom_line(aes(x=time,y=value,group=sim,color=sim,alpha=sim),data=pointc)+theme_bw()+facet_grid(variable ~ .,scales="free_y")
g <- g+scale_color_manual(values=colors)+scale_alpha_manual(values=alphas)
g
```

Goodness of fit: 

```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE} 

library(hydroGOF)


obsc <- pointc %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value)
pointd <- pointc %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame()

oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})  

sims <- sapply(oo,FUN=function(x){x[1,"sim"]})
oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))}) 

oo <- oo %>% do.call(what=rbind)
rownames(oo) <- NULL
knitr::kable(oo)

```




### Winter 2006/2007

Here is a comparison plot:

```{r Winter_2006_2007,eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}

###{r echo=FALSE,out.width='90%', fig.align='center', fig.cap=NULL, fig.height=5,results='asis',warning=FALSE}

library(ggplot2)
library(dplyr)
library(lubridate)
library(purrr)
##library(RColorBrewer)

####  https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=8
color_obs <- "black"
colors <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5",color_obs)
names(colors) <- point$sim %>% unique()

if (colors["obs"]!=color_obs) {
   
   colors[names(colors)!="obs"] <- colors[colors!=color_obs]
   colors["obs"] <- color_obs
   
}
alphas <- array(0.5,length(colors))
names(alphas) <- names(colors)
alphas["obs"] <- 1
####

year <- 2006
start <- "%04d-08-01" %>% sprintf(year) %>% as.Date()
end <- start+years(1)

pointc <- point %>% filter(variable %in% nobs) %>% filter(time >= start & time<=end)

g <- ggplot()+geom_line(aes(x=time,y=value,group=sim,color=sim,alpha=sim),data=pointc)+theme_bw()+facet_grid(variable ~ .,scales="free_y")
g <- g+scale_color_manual(values=colors)+scale_alpha_manual(values=alphas)
g
```

Goodness of fit: 

```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE} 

library(hydroGOF)


obsc <- pointc %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value)
pointd <- pointc %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame()

oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})  

sims <- sapply(oo,FUN=function(x){x[1,"sim"]})
oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))}) 

oo <- oo %>% do.call(what=rbind)
rownames(oo) <- NULL
knitr::kable(oo)

```






### Winter 2007/2008

Here is a comparison plot:

```{r Winter_2007_2009,eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}

###{r echo=FALSE,out.width='90%', fig.align='center', fig.cap=NULL, fig.height=5,results='asis',warning=FALSE}

library(ggplot2)
library(dplyr)
library(lubridate)
library(purrr)
##library(RColorBrewer)

####  https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=8
color_obs <- "black"
colors <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5",color_obs)
names(colors) <- point$sim %>% unique()

if (colors["obs"]!=color_obs) {
   
   colors[names(colors)!="obs"] <- colors[colors!=color_obs]
   colors["obs"] <- color_obs
   
}
alphas <- array(0.5,length(colors))
names(alphas) <- names(colors)
alphas["obs"] <- 1
####

year <- 2007
start <- "%04d-08-01" %>% sprintf(year) %>% as.Date()
end <- start+years(1)

pointc <- point %>% filter(variable %in% nobs) %>% filter(time >= start & time<=end)

g <- ggplot()+geom_line(aes(x=time,y=value,group=sim,color=sim,alpha=sim),data=pointc)+theme_bw()+facet_grid(variable ~ .,scales="free_y")
g <- g+scale_color_manual(values=colors)+scale_alpha_manual(values=alphas)
g
```

Goodness of fit: 

```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE} 

library(hydroGOF)


obsc <- pointc %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value)
pointd <- pointc %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame()

oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})  

sims <- sapply(oo,FUN=function(x){x[1,"sim"]})
oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))}) 

oo <- oo %>% do.call(what=rbind)
rownames(oo) <- NULL
knitr::kable(oo)

```


























### Winter 2008/2009

Here is a comparison plot:

```{r Winter_2008_2009,eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}

###{r echo=FALSE,out.width='90%', fig.align='center', fig.cap=NULL, fig.height=5,results='asis',warning=FALSE}

library(ggplot2)
library(dplyr)
library(lubridate)
library(purrr)
##library(RColorBrewer)

####  https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=8
color_obs <- "black"
colors <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5",color_obs)
names(colors) <- point$sim %>% unique()

if (colors["obs"]!=color_obs) {
   
   colors[names(colors)!="obs"] <- colors[colors!=color_obs]
   colors["obs"] <- color_obs
   
}
alphas <- array(0.5,length(colors))
names(alphas) <- names(colors)
alphas["obs"] <- 1
####

year <- 2008
start <- "%04d-08-01" %>% sprintf(year) %>% as.Date()
end <- start+years(1)

pointc <- point %>% filter(variable %in% nobs) %>% filter(time >= start & time<=end)

g <- ggplot()+geom_line(aes(x=time,y=value,group=sim,color=sim,alpha=sim),data=pointc)+theme_bw()+facet_grid(variable ~ .,scales="free_y")
g <- g+scale_color_manual(values=colors)+scale_alpha_manual(values=alphas)
g
```

Goodness of fit: 

```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE} 

library(hydroGOF)


obsc <- pointc %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value)
pointd <- pointc %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame()

oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})  

sims <- sapply(oo,FUN=function(x){x[1,"sim"]})
oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))}) 

oo <- oo %>% do.call(what=rbind)
rownames(oo) <- NULL
knitr::kable(oo)

```































### Winter 2009/2010

Here is a comparison plot:

```{r Winter_2009_2010,eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}

###{r echo=FALSE,out.width='90%', fig.align='center', fig.cap=NULL, fig.height=5,results='asis',warning=FALSE}

library(ggplot2)
library(dplyr)
library(lubridate)
library(purrr)
##library(RColorBrewer)

####  https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=8
color_obs <- "black"
colors <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5",color_obs)
names(colors) <- point$sim %>% unique()

if (colors["obs"]!=color_obs) {
   
   colors[names(colors)!="obs"] <- colors[colors!=color_obs]
   colors["obs"] <- color_obs
   
}
alphas <- array(0.5,length(colors))
names(alphas) <- names(colors)
alphas["obs"] <- 1
####

year <- 2009
start <- "%04d-08-01" %>% sprintf(year) %>% as.Date()
end <- start+years(1)

pointc <- point %>% filter(variable %in% nobs) %>% filter(time >= start & time<=end)

g <- ggplot()+geom_line(aes(x=time,y=value,group=sim,color=sim,alpha=sim),data=pointc)+theme_bw()+facet_grid(variable ~ .,scales="free_y")
g <- g+scale_color_manual(values=colors)+scale_alpha_manual(values=alphas)
g
```

Goodness of fit: 

```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE} 

library(hydroGOF)


obsc <- pointc %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value)
pointd <- pointc %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame()

oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})  

sims <- sapply(oo,FUN=function(x){x[1,"sim"]})
oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))}) 

oo <- oo %>% do.call(what=rbind)
rownames(oo) <- NULL
knitr::kable(oo)

```







































### Winter 2010/2011

Here is a comparison plot:

```{r Winter_2010_2011,eval=TRUE,echo=FALSE,output=FALSE,results="hide",message=FALSE}

###{r echo=FALSE,out.width='90%', fig.align='center', fig.cap=NULL, fig.height=5,results='asis',warning=FALSE}

library(ggplot2)
library(dplyr)
library(lubridate)
library(purrr)
##library(RColorBrewer)

####  https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=8
color_obs <- "black"
colors <- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5",color_obs)
names(colors) <- point$sim %>% unique()

if (colors["obs"]!=color_obs) {
   
   colors[names(colors)!="obs"] <- colors[colors!=color_obs]
   colors["obs"] <- color_obs
   
}
alphas <- array(0.5,length(colors))
names(alphas) <- names(colors)
alphas["obs"] <- 1
####

year <- 2010
start <- "%04d-08-01" %>% sprintf(year) %>% as.Date()
end <- start+years(1)

pointc <- point %>% filter(variable %in% nobs) %>% filter(time >= start & time<=end)

g <- ggplot()+geom_line(aes(x=time,y=value,group=sim,color=sim,alpha=sim),data=pointc)+theme_bw()+facet_grid(variable ~ .,scales="free_y")
g <- g+scale_color_manual(values=colors)+scale_alpha_manual(values=alphas)
g
```

Goodness of fit: 

```{r eval=TRUE,echo=FALSE,output=FALSE,results='asis',message=FALSE,warning=FALSE} 

library(hydroGOF)


obsc <- pointc %>% filter(sim=="obs") %>% transmute(time=time,variable=variable,obs=value)
pointd <- pointc %>% group_by(sim) %>% left_join(obsc) %>% as.data.frame()

oo <- pointd %>% group_by(sim,variable) %>% group_split() %>% map(as.data.frame) %>% map(function(x) {o <- as.data.frame(gof(sim=x[,"value"],obs=x[,"obs"]));names(o) <- x[1,"variable"];o$sim <- x[1,"sim"];o$gof <- rownames(o);return(o)})  

sims <- sapply(oo,FUN=function(x){x[1,"sim"]})
oo <-   oo %>% tapply(INDEX=sims,FUN=do.call,what="cbind") %>% map(function(x){x[,!(duplicated(names(x)))]}) %>% map(function(x){x[c(c("sim","gof"),names(x)[!(names(x) %in% c("sim","gof"))])]}) %>% map(function(x) {x %>% filter(gof %in% c("MAE","RMSE","KGE"))}) 

oo <- oo %>% do.call(what=rbind)
rownames(oo) <- NULL
knitr::kable(oo)

```

### References

```{r generateBibliography,echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE,print=FALSE,results="hide"}
require("knitcitations")
cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "bibliography.bib")

